---
title: {{{title}}}
author: {{{author}}}
date: {{date}}
repro:
  packages:
    - ggplot2
    - aaronpeikert/repro@adb5fa569
  scripts:
    - R/clean.R
  data:
    mycars: data/mtcars.csv
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(repro)
# load packages from yaml header
automate_load_packages()
# include external scripts
automate_load_scripts()
# load data 'mycars' (ok it is mtcars...)
mycars <- automate_load_data(mycars, read.csv, stringsAsFactors = FALSE)
```

## Repro Package

May I suggest to run `repro::automate()` now? This will create a `Dockerfile` & `Makefile` based on every RMarkdown file in this folder.
The meta information that are provided in each RMarkdown (remember there are special yaml headers for repro) will be evaluted and adjustments will be made accordingly.

If you are unsure whether or not you have `git` `make` & `docker` on your system, try running this in your R console:

```{r, eval=FALSE}
check_git()
check_make()
check_docker()
```

## Analysis

```{r clean}
# see R/clean.R
# this chunk (as long as it is empty, comments don't count) runs external
# code from scripts listed in the YAML
# see also https://yihui.org/knitr/demo/externalization/
```

```{r mpg}
summary(mycars$mpg)
```

## Including Plots

```{r plot, echo=FALSE}
with(mycars, plot(mpg, hp))
```

## Including Fancy Plots

```{r fany-plot, echo=FALSE}
ggplot(mycars, aes(mpg, hp)) +
  geom_point() +
  theme_minimal() +
  NULL
```
